### 2023-04-12 chapters/02-analysis.tex
Compare spectra of different faults in MAFAULDA

\section{Feature engineering}
Large domain knowledge with compared to other areas of machine learning (mechanics - physics)
\subsection{Preprocessing}
\begin{itemize}
\item Detrending - DC removal filter
\item Denoising 
	\begin{itemize}
	\item Gaussian smoothing filter 
	\item Adaptive FIR filter with LMS algorithm
	\item Wavelet thresholding with coif2 or db2
	\end{itemize}
\item Time synchronous averagings
\end{itemize}

@@

\paragraph{Statistical measures}
\begin{itemize}
\item Standard Deviation
\item Max. amplitude
\item RMS amplitude
\item Skewness
\item Kurtosis \\
---
\item Spectral centroid
\item RMS frequency
\item Root variance frequency
\item Spectral kurtosis / Fast kurtogram
\item Harmonic spectral deviation \\
---
\item Energy
\item Spectral negentropy
\item TKEO - Teager-Kaiser energy operator
\end{itemize}

\paragraph{Signal decompositions - sparse approximations}
Matching pursuit algorithm optimalization problem
\begin{itemize}
\item FFT - Short Time Fourier Transform with Hamming window and Welch averaging
\item CWT-SST - Synchrosqueezing Wavelet Transform (vs. Transient-extracting transform)
\item EEMD - Ensemble Empirical Mode Decomposition - to IMF - mode mixing problem
\item WPD - Wavelet Packet Decomposition  - to approximation and detail coef. (Fejer-Korovkin wavelet)
\item EWT - Empirical Wavelet Transform - (Meyer wavelet) 
\end{itemize}

@@

\section{Diagnostics techniques}
Idenification of faulty states in data streams in semi-supervised learning
\subsection{Novelty detection}
\begin{itemize}
\item DenStream (Density based clustering - DBSCAN)
\item Half-space Trees (Isolation forest)
\end{itemize}

\subsection{Classification}
\begin{itemize}
\item kNN + Metric Tree (M-Tree for neighbourhood queries) + Mahalanobis distance / Cosine similarity
\item Naive Bayes + Count-min sketch
\item Label propagation (Temporal label propagation, LabelRankT) - RBF similarity
\end{itemize}

\section{Evaluation Datasets}
\paragraph{MAFAULDA}

\paragraph{CWRU}

>>>>

\section{Feature engineering}
Large domain knowledge with compared to other areas of machine learning (mechanics - physics)
\subsection{Preprocessing}
\begin{itemize}
\item Detrending - DC removal filter
\item Time synchronous averaging
\end{itemize}

@@

\paragraph{Statistical measures}
\begin{itemize}
\item Standard Deviation
\item Max. amplitude
\item RMS amplitude
\item Skewness
\item Kurtosis \\
---
\item Spectral centroid
\item RMS frequency
\item Root variance frequency
\item Spectral kurtosis / Fast kurtogram
\item Harmonics (peaks)
\item Spectral Envelope
\item Harmonic spectral deviation \\
---
\item Energy
\item Spectral negentropy
\item TKEO - Teager-Kaiser energy operator
\end{itemize}

\paragraph{Signal decompositions - sparse approximations}
Matching pursuit algorithm optimalization problem
\begin{itemize}
\item FFT - Short Time Fourier Transform with Hamming window and Welch averaging (cite BP)
\item CWT-SST - Synchrosqueezing Wavelet Transform (vs. Transient-extracting transform)
\item WPD - Wavelet Packet Decomposition  - to approximation and detail coef. (Fejer-Korovkin wavelet)
\item EWT - Empirical Wavelet Transform - (Meyer wavelet) 
\end{itemize}

@@

\section{Diagnostics techniques}
Idenification of faulty states in data streams in semi-supervised learning
\subsection{Novelty detection}
\begin{itemize}
\item Local Outlier Factor, Local Correlation Integral (Anomaly score)
\item DenStream (Density based clustering - DBSCAN)
\item Half-space Trees (Isolation forest)
\end{itemize}

\subsection{Classification}
\begin{itemize}
\item kNN + Metric Tree (M-Tree for neighbourhood queries) + Mahalanobis distance / Cosine similarity /  RBF similarity
\end{itemize}

\section{Evaluation Datasets}
(Pictures of machines)

\paragraph{MAFAULDA}\\
SpectraQuest's Machinery Fault Simulator (MFS) Alignment-Balance-Vibration (ABVT)
50 kHz, 5 sec. recordings, Imbalance, Horizontal/Vertical misalignment, Bearings (Overhang / Underhang) - Inner, Outer, Cage

\paragraph{CWRU}
2 HP (1.492 kW) Reliance Electric motor
Bearings - Inner, Outer
12 kHz, 48 kHz
fan and drive end bearings
Fault diameters of 7 mils, 14 mils, 21 mils, 28 mils, and 40 mils (1 mil=0.001 inches) in diameter were introduced separately at the inner raceway, rolling element (i.e. ball) and outer raceway. 
Faulted bearings were reinstalled into the test motor and vibration data was recorded for motor loads of 0 to 3 horsepower (motor speeds of 1797 to 1720 RPM).

\paragraph{Rotating Shaft}
Shaft -  unbalances of different sizes
4 kHz
